---
title: "`r batch_title`"
subtitle: "Assemblycomparator2 Report"
date: "`r Sys.time()`"
output:
  html_document:
    toc: true
    toc_depth: 2
  #prettydoc::html_pretty:
    theme: spacelab
    #highlight: github
editor_options: 
  chunk_output_type: console
#css: "max-width: 5000px; margin: auto; padding: 1em; line-height: 20px"
---
<style>
table {
  white-space: nowrap; /* Do not wrap table cell contents. */
}
</style>





```{r setup-dependencies, echo=F, message=F, warning=F}

# Dependencies

library(tidyverse)
library(DT)
library(ape)
library(gridExtra)

# I failed trying looking for a package that would robustly midpoint root the tree.
#library(prettydoc)
#library(phytools)
#library(phangorn)



```




```{r setup-debug, echo=F, message=F, warning=F, error = F}



# DEBUG setup for vscode on KTFL running R on ssh to saga
debug = F
if (debug) {
    base_variable = "~/axodines/assemblycomparator2"
    results_directory = "results_ac2"
    setwd("~/axodines/assemblycomparator2/tests/MAGs")
    batch_title = basename(getwd())


    base_variable = "~/axodines/assemblycomparator2"
    results_directory = "results_ac2"
    setwd("~/axodines/assemblycomparator2/tests/synth_rumen")
    batch_title = basename(getwd())
}

```


`r paste0("This report was generated using the results located at ", results_directory, " using the installation at ", base_variable, ".")`


```{r setup-globals, echo=F, message=F, warning=F}


## Global variables
#base_variable = "~/assemblycomparator2/" # I need to find a way of pulling this out of thin air. Maybe there's a way of passing commands through the render call, or I can
report_scripts = paste0(base_variable, "/report_subpipeline/scripts/")




## Global functions

# Print Quick
pq = function(logical, input) {
    if (logical) {
        paste(input)
    } 
}

# A function that returns a new global table enumerator for each call
tableno_var = 0
tableno = function() {
    tableno_var <<- tableno_var + 1
    tableno_var
}

# Same, but for figures
figno_var = 0
figno = function() {
    figno_var <<- figno_var + 1
    figno_var
}


dtable = function(X) {
    
    datatable(X,
        extensions = c("Buttons","KeyTable"), 
        options = list(
            dom = '<"top"B>frtip',
            buttons = list('csv', 'excel'),
            keys = T
        ),
        rownames=F
    )
}

create_dt <- function(x){
    DT::datatable(x,
        extensions = 'Buttons',
        options = list(
            dom = 'Blfrtip',
            buttons = c('copy', 'csv', 'excel'),
            lengthMenu = list(
                c(10,25,50,-1),
                c(10,25,50, "All")
            )
        )
    )
}

custom_dt = function(x, filename = "viewer_", dom = "Blfrtip", ordering = T, width = NULL) {
    
    name = paste(batch_title, filename, sep = "_")
    
    write_tsv(x, paste0(results_directory, "/tables/", name, ".tsv")) # Save a copy on the harddisk for people without browsers.
    
    DT::datatable(
        x,
        options = list(
            dom = dom,
            ordering = ordering,
            #buttons = c('copy', 'csv', 'excel')
            buttons = list(
                list(extend = "csv", filename = name),
                list(extend = "excel", filename = name)
            ),
            lengthMenu = list(
                c(10,25,50,-1),
                c(10,25,50, "All")
            )
        ),
        rownames = F,
        width = width,
        extensions = 'Buttons',

    )
}

paste_ = function(x, ...) {
    paste(x, ..., sep = "_")
}


```


## Samples

```{r sample-overview, echo=FALSE, message=F, warning=F, error = T}

# Import the metadata table
# metadata_translate makes it easy for us later to convert the long paths to short and simple sample names, also highlights potential missing sample analyses

metadata_file = paste0(results_directory, "/metadata.tsv")

metadata_df = read_tsv(metadata_file) %>%
    arrange(sample) # Alphabetical

N = metadata_df %>% nrow() # global variable

# Generate a very simple table which can be used to convert long paths or their basenames to sample names
metadata_translate = metadata_df %>% 
    select(sample, file_long = input_file_fasta) %>%
    mutate(
        file = basename(file_long)
    )


# Present the metadata in the report
metadata_df %>%
    select(input_file, sample) %>% 
    #datatable() # This one is not downloadable
    custom_dt("samples")


    
    
### Sections below
```

*Table `r tableno()`: Overview of the samples analysed in this batch.*


### Report sections

Here is an overview of the number of result files that have been found for each analysis. A report section is only rendered if relevant result files are present for that analysis. 

```{r sample-switchboard, echo=FALSE, message=F, warning=F, error = T}

# Pull all globs and show which are done/presentable

# glob = list()

# glob$assembly_stats = Sys.glob(paste0(results_directory, "/assembly-stats/assembly-stats.tsv"))
# glob$prokka = Sys.glob(paste0(results_directory, "/samples/*/prokka/*.txt"))
# glob$busco = Sys.glob(paste0(results_directory, "/samples/*/busco/*_omesnatoehsnatoe_extract.tsv"))

# Each section of this report is rendered on the basis of the presence of relevant result files.
# In the table below, the globs, and expected number of globs are defined. 
section_definition_table = tribble(

    ~section, ~expectation, ~glob,
    "assembly_stats",    1, Sys.glob(paste0(results_directory, "/assembly-stats/assembly-stats.tsv")),
    "sequence_lengths",  N, Sys.glob(paste0(results_directory, "/samples/*/sequence_lengths/*.tsv")),
    "busco",             N, Sys.glob(paste0(results_directory, "/samples/*/busco/short_summary_extract.tsv")),
    "checkm2",           1, Sys.glob(paste0(results_directory, "/checkm2/quality_report.tsv")),
    "kraken2",           N, Sys.glob(paste0(results_directory, "/samples/*/kraken2/*kraken2_report.tsv")),
    "gtdbtk",            1, Sys.glob(paste0(results_directory, "/gtdbtk/gtdbtk.summary.tsv")),
    #abricate
    #mlst
    "prokka",            N, Sys.glob(paste0(results_directory, "/samples/*/prokka/*.txt")),
    "roary",             1, Sys.glob(paste0(results_directory, "/roary/gene_presence_absence.Rtab")),
    #"roary_summary",             1, Sys.glob(paste0(results_directory, "/roary/summary_statistics.txt")), # Just reuse the presence of the other roary file
    "mashtree",          1, Sys.glob(paste0(results_directory, "/mashtree/mashtree.newick")),
    ) %>%
    #group_by(section) %>%
    mutate(n_files = lengths(glob))






# This list is used out in the individual sections to access the correct files.
glob_list = section_definition_table %>%
    select(section, glob) %>%
    deframe() # Convert to list

# The render variable is finally used to toggle the rendering of each section in the report.
render = lapply(glob_list, function(x) {length(x) > 0})


section_definition_table %>%
    mutate(
        render = case_when(
            n_files > expectation ~ "error", # Hopefully this won't ever happen
            n_files == expectation ~ "🟢 yes",
            n_files > 0 ~ "🟡 yes, partially",
            n_files == 0 ~ "🔴 no"),
        `n / expected` = paste0(n_files, " / ", expectation)
    ) %>%
    select(section, `n / expected`, render) %>%
    custom_dt("sections", dom = "t", ordering = F, width = 500)

# Define a variable that can be used to query whether each section of the report should be rendered


# By the way: Remember to have double new lines between the dash-lines (---) and the r child chunks. Otherwise the parsing gets weird, with figure texts becoming headers.

```


*Table `r tableno()`: Overview of sections that are rendered in this report. "n / expected" shows the number of analysis files versus how many are expected to be present. Sections are only rendered if relevant files exist. Analyses that perform comparisons between samples generally only output one set of results independent on the number of input files*



---



```{r child = paste0(report_scripts, "section_assembly_stats.rmd"), eval = render$assembly_stats}
```

```{r child = paste0(report_scripts, "section_sequence_lengths.rmd"), eval = render$sequence_lengths}
```

```{r child = paste0(report_scripts, "section_busco.rmd"), eval = render$busco}
```

```{r child = paste0(report_scripts, "section_checkm2.rmd"), eval = render$checkm2}
```

```{r child = paste0(report_scripts, "section_kraken2.rmd"), eval = render$kraken2}
```

```{r child = paste0(report_scripts, "section_gtdbtk.rmd"), eval = render$gtdbtk}
```

```{r child = paste0(report_scripts, "section_prokka.rmd"), eval = render$prokka}
```

```{r child = paste0(report_scripts, "section_roary.rmd"), eval = render$roary}
```

```{r child = paste0(report_scripts, "section_mashtree.rmd"), eval = render$mashtree}
```












------------------------------------------------------------------------

The [assemblycomparator2](https://github.com/cmkobel/assemblycomparator2#assemblycomparator2) pipeline and report is developed by [Oliver Hansen](https://github.com/oliverh2020) & [Carl M. Kobel](https://github.com/cmkobel) `version 2.4.0`.