## Antimicrobial Resistance

`rule abricate` Using [Abricate](https://github.com/tseemann/abricate#abricate), the assemblies are scanned for known resistance genes in the ncbi, card, plasmidfinder and vfdb antimicrobial resistance databases.


#### NCBI AMRFinder

```{r abricate-ncbi, echo = F, message = F, warning = F, error = T}

#glob_list$abricate

# I know there is a summary, but making sure that everything is parsed as numbers is just easier if I do my own pivot.
#abricate_ncbi = read_tsv("results_ac2/abricate/ncbi_detailed.tsv", na = ".") %>%
#abricate_ncbi = read_tsv(glob_list$abricate, na = ".") %>%
abricate_ncbi = read_tsv(glob_list$abricate[grepl("ncbi_", glob_list$abricate)], na = ".") %>%
    #rename(file_long = `#FILE`) #%>%
    mutate(file = basename(`#FILE`)) %>%
    select(file, GENE, `%COVERAGE`) %>%


    # Count number of genes in each sample
    group_by(file) %>%
    mutate(n = n()) %>%
    ungroup() %>%

    # Finally pivot to summarize
    pivot_wider(id_cols = c(file, n), names_from = GENE, values_from = `%COVERAGE`)



metadata_translate %>% 
    select(sample, file) %>%
    left_join(abricate_ncbi, by = "file") %>%
    select(-file) %>%
    mutate(n = coalesce(n, 0)) %>% # the count will be empty for samples without matches otherwise
    custom_dt("abricate_ncbi")


```


*Table `r tableno()`: Table of NCBI Resistance gene calls called with [NCBI AMRFinder](https://www.ncbi.nlm.nih.gov/pmc/articles/PMC6811410/).*

---

#### VFDB

```{r abricate-vfdb, echo = F, message = F, warning = F, error = T}

# I know there is a summary, but making sure that everything is parsed as numbers is just easier if I do my own pivot.
abricate_vfdb = read_tsv(glob_list$abricate[grepl("vfdb_", glob_list$abricate)], na = ".") %>%
    #rename(file_long = `#FILE`) #%>%
    mutate(file = basename(`#FILE`)) %>%
    select(file, GENE, `%COVERAGE`) %>%


    # Count number of genes in each sample
    group_by(file) %>%
    mutate(n = n()) %>%
    ungroup() %>%

    # Finally pivot to summarize
    pivot_wider(id_cols = c(file, n), names_from = GENE, values_from = `%COVERAGE`)



metadata_translate %>% 
    select(sample, file) %>%
    left_join(abricate_vfdb, by = "file") %>%
    select(-file) %>%
    mutate(n = coalesce(n, 0)) %>% # the count will be empty for samples without matches otherwise
    custom_dt("abricate_vfdb")


```

*Table `r tableno()`: Table of [VFDB](http://www.mgc.ac.cn/VFs/main.htm) virulence factor calls: "An integrated and comprehensive online resource for curating information about virulence factors of bacterial pathogens".*





---