---
title: "R Notebook"
output: html_notebook
---

```{r}
# Preamble
library(tidyverse)
# setwd("~/assemblycomparator2/tests/E._faecium_plasmids/")
```


```{r}
# Register inputs
file_prefix = "../assemblycomparator2/tests/E._faecium_plasmids/output_asscom2/"
possible_inputs = tribble(
    ~section,       ~file,
    "metadata",     paste0(file_prefix, "metadata.tsv"),
    
    "abricate",     paste0(file_prefix, "abricate/card_detailed.tsv"),
    "abricate",     paste0(file_prefix, "abricate/card_summarized.tsv"),
    
    "fse",          paste0(file_prefix, "fse/data.txt"),
)
```


```{r, echo=TRUE}
# Mark if the files exist
inputs_df = possible_inputs %>%
    mutate(section = factor(section, levels = unique(section)), # keep the initial ordering of the sections.
           exists = file.exists(file), 
           basename = basename(file)) |> 
    select(section, basename, exists, file)

inputs_df

```


```{r}

# Make a list that can easily be intuitively accessed with R base syntax
inputs = inputs_df |> 
    group_by(name = section) |> 
    summarize(value = all(exists)) |> 
    pivot_wider()

inputs
```

`r if (inputs$metadata) { "" }`
`r if (inputs$metadata) { "# Section Metadata" }`
`r if (inputs$metadata) { "In this section the metadata will briefly be presented." }`





`r if (inputs$abricate) { "" }`
`r if (inputs$abricate) { "# Section Abricate" }`
`r if (inputs$abricate) { "In this section we will present the output from abricate." }`



`r if (inputs$fse) { "" }`
`r if (inputs$fse) { "# Section Abricate" }`
`r if (inputs$fse) { "In this section we will present the output from fse." }`




