---
title: "`r batch_title`"
subtitle: "CompareM2 Report"
date: "`r Sys.time()`"
output:
  html_document:
    toc: true
    toc_depth: 2
  #prettydoc::html_pretty:
    theme: flatly
    #highlight: github
    center: false
editor_options: 
  chunk_output_type: console
#css: "max-width: 5000px; margin: auto; padding: 1em; line-height: 20px"
---
<style>

.main-container {
    margin-left: 60px; /* was auto */
    margin-top: 37px; /* was 0 */
}

table {
  white-space: nowrap; /* Do not wrap table cell contents. */
}

/* Use serif fonts for text. Not in tables. */
p {
    color: black;
    font-family: Georgia,"Times New Roman",Times,serif;
    font-size: 16px;
}


.shaded {
    color: #929292;
}

</style>


```{r setup-dependencies, echo=F, message=F, warning=F}

# Dependencies

library(tidyverse)
library(DT)
library(ape)
library(rmarkdown)


```




```{r setup-debug, echo=F, message=F, warning=F, error = F}



# DEBUG setup for vscode on KTFL running R on ssh to saga
debug = F
if (debug) {
        
    # panaroo on mac
    base_variable = "~/comparem2/"
    output_directory = "results_comparem2_panaroo"
    setwd("~/comparem2/")
    batch_title = basename(getwd())
    
    # base on thyla
    base_variable = "~/comparem2/"
    output_directory = "results_comparem2"
    setwd("~/comparem2/")
    batch_title = basename(getwd())
    
    
    # eggnog caroline wh on thyla
    base_variable = "~/comparem2"
    output_directory = "/home/thylakoid/PhD/47_CEH/CWH_mags/cwh_mags_renamed_TR/results_comparem2"
    setwd("~/comparem2/")
    batch_title = basename(getwd())
    
    # e faecium on thyla
    base_variable = "~/comparem2"
    output_directory = "/home/thylakoid/comparem2/tests/E._faecium/results_comparem2"
    setwd("~/comparem2/")
    batch_title = basename(getwd())
    
    # e faecium weird
    base_variable = "~/comparem2"
    setwd(base_variable)
    output_directory = "/home/thylakoid/comparem2/test_comparem2_install/test_comparem2_install/results_comparem2"
    batch_title = basename(getwd())
    
    
    
    # checkci that shows weird snp-dists error
    base_variable = "~/comparem2"
    setwd(base_variable)
    batch_title = basename(getwd())
    output_directory = "/home/thylakoid/comparem2/check_core_for_ci/results_comparem2"
    
    
}

```

`r paste0("This report was generated by ", Sys.getenv("USER"), " on ", Sys.time(), " using CompareM2 v", version_string, " based at ", base_variable, ". The content is dynamically rendered based on the results located at ", current_dir, ".")`


```{r setup-globals, echo=F, message=F, warning=F}


## Global variables
#base_variable = "~/comparem2/" # I need to find a way of pulling this out of thin air. Maybe there's a way of passing commands through the render call, or I can
report_scripts = paste0(base_variable, "/dynamic_report/workflow/scripts/")


## Global functions

# A function that returns a new global table enumerator for each call
tableno_var = 0
tableno = function() {
    tableno_var <<- tableno_var + 1
    tableno_var
}

# Same, but for figures
figno_var = 0
figno = function() {
    figno_var <<- figno_var + 1
    figno_var
}

# This function returns a data table with custom settings.
custom_dt = function(x, filename = "viewer_", dom = "Blfrtip", ordering = T, width = NULL, show_n = 10, save_tsv = TRUE) {
    
    name = paste(batch_title, filename, sep = "__")
    
    if (save_tsv) {
        write_tsv(x, paste0(output_directory, "/tables/", name, ".tsv")) # Save a copy on the harddisk for people without browsers.
    }
    
    DT::datatable(
        x,
        options = list(
            dom = dom,
            ordering = ordering,
            #buttons = c('copy', 'csv', 'excel')
            buttons = list(
                list(extend = "csv", filename = name),
                list(extend = "excel", filename = name)
            ),
            lengthMenu = list(
                c(show_n ,25, 50, -1),
                c(show_n ,25, 50, "All")
            )
        ),
        rownames = F,
        width = width,
        extensions = 'Buttons',

    )
}

cm2_save_plot = function(content) {
    name = paste(batch_title, content, sep = "__")
    ggsave(filename = paste0(output_directory, "/tables/", name, ".pdf")) # Save a vector version.

}




```



### Sample overview

```{r sample-overview, echo=FALSE, message=F, warning=F, error = T}

# Import the metadata table
# metadata_translate makes it easy for us later to convert the long paths to short and simple sample names, also highlights potential missing sample analyses

metadata_file = paste0(output_directory, "/metadata.tsv")

metadata_df = read_tsv(metadata_file) %>%
    arrange(sample)  # Alphabetical

N = metadata_df %>% nrow() # Global variable.

# Generate a very simple table which can be used to convert long paths or their basenames to sample names
metadata_translate_lexicographic = metadata_df %>% 
    select(sample, file_long = input_file_copy) %>%
    mutate(
        file = basename(file_long),
        index = 1:n() # Using a numerical index is so much easier I think.
        #index = n():1 # Using a numerical index is so much easier I think. Since the tree is drawn from the bottom we should reverse the direction of the index.
        
    ) %>% 
    relocate(index)

ARRANGEMENT = "lexicographic" # Global variable.

# If mashtree has been run, we might as well order the samples by the order of the tree. This is of course only a luxury, and not a dependency. In case the user has trouble running mashtree -which is unlikely- it is great to have a workaround which is to use the alphabetical order which is already defined above.

mashtree_voluntary_dependency = paste0(output_directory, "/mashtree/mashtree.newick")
if (file.exists(mashtree_voluntary_dependency)) {
    
    # Overwrite metadata_translate in case the newick file from mashtree exists.
    # But 
    metadata_translate = read_lines(mashtree_voluntary_dependency) %>% 
        str_split(",") %>% unlist() %>% 
        str_remove("^\\(+") %>% # Remove head
        str_remove("\\:.+$")  %>% # Remove tail
        enframe(name = "index", value = "sample") %>% 
        mutate(index = rev(index)) %>%
        arrange(index) %>% 
        
        left_join(metadata_translate_lexicographic %>% select(-index), by = "sample") # add metadata_translate without its lexicographic index.
    
    ARRANGEMENT = "phylogenetic"
        
} else { # In case mashtree didn't succeed (for instance, if one file is not a genome and thus crashes mashtree), we want to continue with a simple lexicographic ordering of the samples.
    metadata_translate = metadata_translate_lexicographic
}



    
if(ARRANGEMENT == "lexicographic") {
    arrangement_text = "Because mashtree has not run (successfully), the samples are arranged alphabetically." # Lexicographically sounds so nerdy.
} else { # == "phylogenetic"
    arrangement_text = "Because mashtree has run, the samples are arranged by the order of the mashtree output."
}


# Present the metadata in the report
metadata_translate  %>% 
    select(index, sample, file) %>% 
    custom_dt("samples")

    


### Sections below
```

*Table `r tableno()`: Overview of the samples analysed in this batch. `r paste(arrangement_text)`*


### Report sections

Here is an overview of the number of result files that have been found for each analysis. A report section is only rendered if relevant result files are present for that analysis. Each section can be triggered to run by calling comparem2 with a trailing `--until <section>`

```{r sample-switchboard, echo=FALSE, message=F, warning=F, error = T}

# Pull all globs and show which are done/presentable

# glob = list()

# glob$assembly_stats = Sys.glob(paste0(output_directory, "/assembly-stats/assembly-stats.tsv"))
# glob$prokka = Sys.glob(paste0(output_directory, "/samples/*/prokka/*.txt"))

# Each section of this report is rendered on the basis of the presence of relevant result files.
# In the table below, the globs, and expected number of globs are defined. 
section_definition_table = tribble(

    ~section,            ~expectation,                         ~glob,

    "assembly_stats",    1, Sys.glob(paste0(output_directory, "/assembly-stats/assembly-stats.tsv")),
    "sequence_lengths",  N, Sys.glob(paste0(output_directory, "/samples/*/sequence_lengths/*.tsv")),
    "checkm2",           1, Sys.glob(paste0(output_directory, "/checkm2/quality_report.tsv")),
    "gtdbtk",            1, Sys.glob(paste0(output_directory, "/gtdbtk/gtdbtk.summary.tsv")),
    "mlst",              1, Sys.glob(paste0(output_directory, "/mlst/mlst.tsv")),
    "amrfinder",         N, Sys.glob(paste0(output_directory, "/samples/*/amrfinder/*.tsv")),
    "prokka",            N, Sys.glob(paste0(output_directory, "/samples/*/prokka/*.txt")),
    "eggnog",            N, Sys.glob(paste0(output_directory, "/samples/*/eggnog/*.emapper.annotations")),
    "kegg_pathway",      1, Sys.glob(paste0(output_directory, "/kegg_pathway/kegg_pathway_enrichment_analysis.tsv")),
    "dbcan",             N, Sys.glob(paste0(output_directory, "/samples/*/dbcan/dbcan-sub.hmm.out")),
    "gapseq_find",            N, Sys.glob(paste0(output_directory, "/samples/*/gapseq/*-all-Pathways.tbl")),
    "panaroo",           1, Sys.glob(paste0(output_directory, "/panaroo/gene_presence_absence.Rtab")), # This also counts for the panaroo summary file.
    "snp_dists",         1, Sys.glob(paste0(output_directory, "/snp-dists/snp-dists.tsv")),
    "mashtree",          1, Sys.glob(mashtree_voluntary_dependency) # Reuse from earlier.
    
    ) %>%
    mutate(n_files = lengths(glob))






# This list is used out in the individual sections to access the correct files.
glob_list = section_definition_table %>%
    select(section, glob) %>%
    deframe() # Convert to list

# The render variable is finally used to toggle the rendering of each section in the report.
render = lapply(glob_list, function(x) {length(x) > 0}) # Anything more than one file, will trigger the rendering.


section_definition_table %>%
    mutate(
        render = case_when(
            n_files > expectation ~ "🟢 yes, extra", # This should only happen if samples are deleted from the input directory. But isn't a problem as we're left joining onto the metadata table.
            n_files == expectation ~ "🟢 yes",
            n_files > 0 ~ "🟡 yes, partially",
            n_files == 0 ~ "🟠 no"),
        `n / expected` = paste0(n_files, " / ", expectation)
    ) %>%
    select(section, `n / expected`, render) %>%
    custom_dt("sections", dom = "t", ordering = F, width = 500, show_n = nrow(section_definition_table))
    #custom_dt("sections", ordering = F, width = 500)

# Define a variable that can be used to query whether each section of the report should be rendered


# By the way: Remember to have double new lines between the dash-lines (---) and the r child chunks. Otherwise the parsing gets weird, with figure texts becoming headers.

# Parse versions



df_versions = tibble("versions" = read_lines(Sys.glob(paste0(output_directory, "/versions.txt")))) 


```



---



```{r section_assembly_stats, child = paste0(report_scripts, "section_assembly_stats.rmd"), eval = render$assembly_stats}
```

```{r section_sequence_lengths, child = paste0(report_scripts, "section_sequence_lengths.rmd"), eval = render$sequence_lengths}
```


```{r section_checkm2, child = paste0(report_scripts, "section_checkm2.rmd"), eval = render$checkm2}
```



```{r section_mlst, child = paste0(report_scripts, "section_mlst.rmd"), eval = render$mlst}
```

```{r section_amrfinder, child = paste0(report_scripts, "section_amrfinder.rmd"), eval = render$amrfinder}
```

```{r section_prokka, child = paste0(report_scripts, "section_prokka.rmd"), eval = render$prokka}
```



```{r section_eggnog, child = paste0(report_scripts, "section_eggnog.rmd"), eval = render$eggnog}
```

```{r section_kegg_pathway, child = paste0(report_scripts, "section_kegg_pathway.rmd"), eval = render$kegg_pathway}
```

```{r section_dbcan, child = paste0(report_scripts, "section_dbcan.rmd"), eval = render$dbcan}
```

```{r section_gapseq_find, child = paste0(report_scripts, "section_gapseq_find.rmd"), eval = render$gapseq_find}
```




```{r section_panaroo, child = paste0(report_scripts, "section_panaroo.rmd"), eval = render$panaroo}
```



```{r section_gtdbtk, child = paste0(report_scripts, "section_gtdbtk.rmd"), eval = render$gtdbtk}
```

```{r section_snp_dists, child = paste0(report_scripts, "section_snp_dists.rmd"), eval = render$snp_dists}
```

```{r section_mashtree, child = paste0(report_scripts, "section_mashtree.rmd"), eval = render$mashtree}
```



### Versions

The table below shows the version information for the tools used to produce these results.

```{r versions, echo=FALSE, message=F, warning=F, error = T}

df_versions %>%
    mutate(versions = str_replace_all(versions, " +", " ")) %>%
    separate_wider_delim(versions, delim = " ", names = c("tool", "version"), too_many = "merge") %>%
    custom_dt("versions", dom = "t", ordering = F, width = 500, show_n = nrow(df_versions))

```


---

<p class = "shaded">[CompareM2](https://github.com/cmkobel/comparem2) v`r version_string` genomes-to-report pipeline. Copyright (C) 2019-2025 [contributors](https://comparem2.readthedocs.io/en/latest/82%20contributors/) GNU GPL v3.</p>

