## BUSCO

`rule busco`

```{r busco, echo=FALSE, message=F, warning=F, error = T}

#setwd("~/assemblycomparator2") # DEBUG


busco_raw = read_delim(glob_list$busco, delim = ": ", col_names = c("name", "value"))
busco_df = busco_raw %>% 
    mutate(id = (name == "in") %>% as.integer() %>% cumsum()) %>% 
    mutate(value = str_remove(value, ",$")) %>% 
    
    pivot_wider(id_cols = id)  %>% 
    select(-id)  %>% 
    rename(file = `in`, lineage = name) %>% 
    
    mutate(file = basename(file) %>% str_remove("\\.faa$")) %>% 
    
    separate(one_line_summary, c("pre_CS", "D", "F", "M", "n"), sep = ",", extra = "drop") %>% 
    separate(pre_CS, c("C", "S"), "\\[") %>% 
    mutate(D = str_remove(D, "\\]")) %>% 
    
    mutate(
        C = str_extract(C, "\\d+.\\d+") %>% as.numeric,
        S = str_extract(S, "\\d+.\\d+") %>% as.numeric,
        D = str_extract(D, "\\d+.\\d+") %>% as.numeric,
        F = str_extract(F, "\\d+.\\d+") %>% as.numeric,
        M = str_extract(M, "\\d+.\\d+") %>% as.numeric,
        n = str_extract(n, "\\d+") %>% as.numeric
    ) %>% 
    group_by(file) %>% 
    arrange(desc(C)) %>% 
    mutate(rank = 1:n()) %>% 
    ungroup()

# Present table
busco_df_meta = metadata_translate %>%
    left_join(busco_df %>% filter(rank == 1), by = c("sample" = "file")) %>%
    select(-file, -file_long, -rank) %>%
    arrange(lineage)


busco_df_meta %>% 
    custom_dt("busco")

```

*Table `r tableno()`: Table of [BUSCO](https://busco.ezlab.org/) "BUSCO estimates the completeness and redundancy of processed genomic data based on universal single-copy orthologs.". The following columns are printed as percents [%]: C: Complete, S: Complete and single-copy, D: Complete and duplicated, F: Fragmented, M: Missing, n: Total BUSCO groups searched. For each sample, only the best lineage match (in terms of completeness) is shown.*


```{r busco-plot, echo = F, message = F, warning = F, error = T, fig.height = max(1.8, (N*0.2)+0.3), fig.width = 10}

busco_df_meta %>%
    select(index, sample, `S` = S, `D` = D, F, M) %>%
    pivot_longer(-c(sample, index)) %>%
    mutate(name = factor(name, levels = c("M", "F","D", "S"))) %>%
    ggplot(aes(value, reorder(sample, desc(index)), fill = name)) + 
    geom_bar(position = "stack", stat = "identity") + 
    scale_fill_manual(
        values = c(rgb(235/255, 73/255, 71/255), rgb(241/255, 230/255, 76/255), rgb(67/255, 151/255, 202/255), rgb(98/255, 185/255, 234/255)),
        guide = guide_legend(reverse = TRUE)) +
    labs(
        x = "percent",
        y = "sample",
        fill = "Busco\nclass"
    ) + 
    theme_classic() +
    theme(legend.position = "bottom") 


```

*Fig. `r figno()`: BUSCO results visualized. Legend: S: Complete and single-copy; D: Complete and duplicated; F: Fragmented; M: Missing. For each sample, only the best lineage match (in terms of completeness) is shown.*


---